Online resolving assembly graph by ONT long reads data

### 2019-06-13 paper.tex
abc
more methods

%Authors
\author[1,$\ast$]{Son Hoang Nguyen}
%\author[]{Minh Duc Cao}
\author[1,$\ast$]{Lachlan Coin}

%Affiliation
\affil[1]{Institute for Molecular Bioscience, the University of Queensland, 
St Lucia, Brisbane, QLD 4072 Australia}

\correspondingauthor{
\textsuperscript{$\ast$}
To whom correspondence should be addressed. 
E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Materials and Methods}

Basically the work flow of \npgraph{} can be divided into 3 main phases: abundance binning, graph resolving and assembly output. 
The first step will try to bin the contigs into different groups of \emph{population} based on their coverage. 
Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
The binning phase would assist to differentiate between repetitive contigs and unique ones. By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time. Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.

@@

Assume there are 2 Poisson distribution $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$ 
The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.

>>>>

%Authors
\author[1,$\ast$]{Son Hoang Nguyen}
\author[2]{Minh Duc Cao}
\author[1,$\ast$]{Lachlan Coin}

%Affiliation
\affil[1]{Institute for Molecular Bioscience, the University of Queensland, 
St Lucia, Brisbane, QLD 4072 Australia}
\affil[2]{4catalyzer}
\correspondingauthor{
\textsuperscript{$\ast$}
To whom correspondence should be addressed. 
E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Methods}

Basically the work flow of \npgraph{} consists of 3 main modules: abundance binning, graph resolving and assembly output. 
The first step is to bin the contigs into different groups of \emph{population} based on their coverage. 
Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
The binning phase would assist to differentiate between repetitive contigs and unique ones. By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time. Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.

@@

Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$ 
The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
